%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wenneker Resume/CV
% LaTeX Template
% Version 1.1 (19/6/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com) with extensive modifications by 
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper,12pt]{memoir} % Font and paper size

\input{structure.tex} % Include the file specifying document layout and packages

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION 
%----------------------------------------------------------------------------------------

\userinformation{ % Set the content that goes into the sidebar of each page
\begin{flushright}
\small % Smaller font size
Hayden McAlister \\ % Your name
\Sep % Some whitespace
\textbf{Email} \\
\url{haydenmcalister49@gmail.com} \\ % Your email address
\Sep % Some whitespace
\textbf{Phone} \\
022 120 8324 \\ % Your phone number
\Sep % Some whitespace
\textbf{Github} \\
\url{https://github.com/hmcalister}
\vfill % Whitespace under this block to push it up under the photo
\end{flushright}
}

%----------------------------------------------------------------------------------------

\begin{document}

\userinformation % Print your information in the left column

\framebreak % End of the first column

%----------------------------------------------------------------------------------------
%	HEADING
%----------------------------------------------------------------------------------------

\cvheading{Hayden McAlister} % Large heading - your name

\cvsubheading{Software Engineer} % Subheading - your occupation/specialization

%----------------------------------------------------------------------------------------
%	ABOUT ME
%----------------------------------------------------------------------------------------

\aboutme{About Me}{I am a Masters student of Computer Science at the University of Otago. 
My research has focused on artificial intelligence, neural networks, and high dimensional dynamic systems. \\
% My other interests in the field include physics simulations, data science, and natural language processing, among many others. 
I enjoy investigating new ideas, trying new technologies, and solving problems both mathematical and engineering in nature. 
I have a strong background in computer science, as well as mathematics and physics, which has helped me develop problem solving skills.}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\CVSection{Education}

%------------------------------------------------

\CVItem{MSc. Computer Science}{
	University of Otago, 2023 \\
	Thesis: \textit{Energy and the Hopfield Network: A Complementary Perspective}
}



%------------------------------------------------

\CVItem{BSc(Hons), 1st Degree. Computer Science}{
	University of Otago, 2022 \\
	Dissertation: \textit{Sequential Learning in Hopfield Networks}
}


%------------------------------------------------

\CVItem{BSc. Major in Computer Science, Minors in Physics, Mathematics}{
	University of Otago, 2019-2021\\
}

%------------------------------------------------

\Sep % Extra whitespace after the end of a major section

%----------------------------------------------------------------------------------------
%	Research Projects
%----------------------------------------------------------------------------------------

\CVSection{Research Projects}

%------------------------------------------------

\CVItem{2022-2023, \textit{Interpretability of Neural Networks}, University of Otago}{
	Research project in interpretability of convolutional neural networks. \\
	Gained a lot of experience with very low level Tensorflow and other machine learning libraries. Worked independently to achieve project goals.
}

\CVItem{2023, \textit{Handwriting Analysis Project}, University of Otago}{
	Group research project in handwriting analysis. Attempted to classify handwriting quality using a variety of metrics.\\
	Gained experience with data cleaning, signal processing, data visualization, and model comparisons.
}\\

\CVItem{2022, \textit{Natural Language Processing Project}, University of Otago}{
	Group research project in natural language processing. Goal was to create methods of measuring similarities between documents with respect to different metrics.\\
	Gained experience with data cleaning, data processing, natural language processing, and natural language tools.
}

%------------------------------------------------

\clearpage % Start a new page

\userinformation % Print your information in the left column

\framebreak % End of the first column

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\CVSection{Experience}

%------------------------------------------------

\CVItem{2021-2023, \textit{Lab Demonstrating (Various Papers)}, University of Otago}{
	Involved presenting computer science topics to students. With more experience also involved creating and refining teaching resources for labs.\\
	Detailed achievements:
	\begin{itemize}
		\item Demonstrated for the papers:
		\begin{itemize}
			\item COSC201: Algorithms and Data Structures
			\item COSC202: Software Development
			\item COSC203: Web, Databases, and Networks
			\item COSC204: Computer Systems and Security
			\item COSC301: Network Management and Security
			\item COSC343: Artificial Intelligence
		\end{itemize}
		\item Gained experience working with a team 
		\item Gained experience explaining difficult concepts to the point of deep understanding
	\end{itemize}
}

\CVItem{2020-2023, \textit{Tutoring}, Freelance} {
	Freelance tutoring for various subjects about the university. Specifically tutored in the fields of Computer Science, Mathematics, and Physics.
}

\CVItem{2020 - 2022, \textit{IT + Web Design}, STMSNZ}{
	Detailed achievements:
	\begin{itemize}
		\item Designed and created custom websites
		\item Aided with many mundane IT tasks, e.g.:
		\begin{itemize}
			\item Email clients
			\item Software bugs
			\item Fixing user errors
		\end{itemize}
	\end{itemize}
}

\Sep % Extra whitespace after the end of a major section

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\CVSection{Software Development Skills}

%------------------------------------------------

\CVItem{Programming}
{\begin{tabular}{p{0.2\textwidth} p{0.2\textwidth} p{0.2\textwidth}}
\bluebullet Python &  \bluebullet Go & \bluebullet Rust\\
\bluebullet Java &  \bluebullet C/C++ & \bluebullet Matlab\\
\bluebullet Shell &  \bluebullet JS + Frameworks\\
\end{tabular}}

%------------------------------------------------

\CVItem{Machine Learning + Data Science}
{\begin{tabular}{p{0.2\textwidth} p{0.2\textwidth} p{0.2\textwidth}}
 \bluebullet Tensorflow &  \bluebullet Pytorch & \bluebullet SpaCy\\
 \bluebullet Dash &  \bluebullet NumPy & \bluebullet SciPy\\
 \bluebullet Pandas &  \bluebullet Polars & \bluebullet SQL\\
\end{tabular}}

%------------------------------------------------

\CVItem{Databases}
{\begin{tabular}{p{0.2\textwidth} p{0.2\textwidth} p{0.2\textwidth}}
 \bluebullet MySQL &  \bluebullet SQLite & \bluebullet MongoDB\\
 \bluebullet Cassandra &  \bluebullet Monarch & \bluebullet GraphQL\\
\end{tabular}}

%------------------------------------------------

\CVItem{Other Technologies}
{\begin{tabular}{p{0.2\textwidth} p{0.2\textwidth} p{0.2\textwidth}}
 \bluebullet Git/GitHub &  \bluebullet AWS/Cloud & \bluebullet Bash/Shell\\
 \bluebullet gRPC &  \bluebullet Docker & \bluebullet Kubernetes\\
 \bluebullet Terraform &  \\
\end{tabular}}

%------------------------------------------------


\Sep % Extra whitespace after the end of a major section

%----------------------------------------------------------------------------------------
%	NEW PAGE DELIMITER
%	Place this block wherever you would like the content of your CV to go onto the next page
%----------------------------------------------------------------------------------------

\clearpage % Start a new page

\userinformation % Print your information in the left column

\framebreak % End of the first column

%----------------------------------------------------------------------------------------
%	AWARDS
%----------------------------------------------------------------------------------------

\CVSection{Awards}

%------------------------------------------------

\CVItem{2023, \textit{Master's Research Scholarship}, University of Otago}{Awarded to students with high academic achievement moving into Masters research.}
\\
\CVItem{2021, \textit{Sir George Grey Senior Scholarship}, University of Otago}{Awarded to the top Bachelors student in the Division of Science.}
\\
\CVItem{2021, 2022, \textit{Summer Research Scholarship}, University of Otago}{Awarded to students who undertake a research project over summer.}
\\
\CVItem{2020, \textit{Robert Jack Physics Prize (200 Level)}, University of Otago}{Awarded to the top student in 200-level physics.}
\\
\CVItem{2019, \textit{Academic Excellence Entrance Scholarship}, University of Otago}{Awarded to the students with high academic achievement entering the University of Otago.}
\\
\CVItem{2019, \textit{Gordon Jupp Memorial Prize in Physics}, University of Otago}{Awarded to the top student in 100-level physics.}
\\
\CVItem{2019, \textit{Dux Scholarship}, Otago Boys High School}{Awarded to the Dux of Otago Boys High School to study at university.}

%------------------------------------------------

\Sep % Extra whitespace after the end of a major section

%----------------------------------------------------------------------------------------
%	INTERESTS
%----------------------------------------------------------------------------------------

\CVSection{Interests}

%------------------------------------------------

\CVItem{Professional}{Machine Learning, Neural Networks, Data Science, Data Visualization, Software Engineering, Software Development, Software Scalability}

%------------------------------------------------

\CVItem{Personal}{Mathematics, Physics, History, Guitar, Dungeons and Dragons, Magic: The Gathering}

%------------------------------------------------

\Sep % Extra whitespace after the end of a major section

%----------------------------------------------------------------------------------------

\end{document}
