%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wenneker Resume/CV
% LaTeX Template
% Version 1.1 (19/6/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com) with extensive modifications by 
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper,12pt]{memoir} % Font and paper size

\input{structure.tex} % Include the file specifying document layout and packages

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION 
%----------------------------------------------------------------------------------------

\userinformation{ % Set the content that goes into the sidebar of each page
\begin{flushright}
\small % Smaller font size
Hayden McAlister \\ % Your name
\Sep % Some whitespace
\textbf{Email} \\
\url{haydenmcalister49@gmail.com} \\ % Your email address
\Sep % Some whitespace
\textbf{Phone} \\
022 120 8324 \\ % Your phone number
\Sep % Some whitespace
\textbf{Github} \\
\url{https://github.com/hmcalister}
\vfill % Whitespace under this block to push it up under the photo
\end{flushright}
}

%----------------------------------------------------------------------------------------

\begin{document}

\userinformation % Print your information in the left column

\framebreak % End of the first column

%----------------------------------------------------------------------------------------
%	HEADING
%----------------------------------------------------------------------------------------

\cvheading{Hayden McAlister} % Large heading - your name

\cvsubheading{Postgraduate Student - University of Otago} % Subheading - your occupation/specialization

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\CVSection{Education}

%------------------------------------------------

\CVItem{MSc. Computer Science}{
	University of Otago, 2023 (In Progress) \\
	Thesis: \textit{Energy and the Hopfield Network: A Complementary Perspective}
}

%------------------------------------------------

\CVItem{BSc(Hons), 1st Degree. Computer Science}{
	University of Otago, 2022 \\
	Dissertation: \textit{Sequential Learning in Hopfield Networks}
}


%------------------------------------------------

\CVItem{BSc. Major in Computer Science, Minors in Physics, Mathematics}{
	University of Otago, 2019-2021\\
}

%------------------------------------------------

\Sep % Extra whitespace after the end of a major section

%----------------------------------------------------------------------------------------
%	Research Projects
%----------------------------------------------------------------------------------------

\CVSection{Research Projects}

%------------------------------------------------

\CVItem{2022-2023, \textit{Interpretability of Deep Neural Networks}, University of Otago}{
	Summer research project into the interpretability of deep neural networks with a focus on convolutional networks. \\
	Found current state of the art interpretability methods are highly sensitive to hyperparameters. Also found interpretability methods have some relation to weight importance measures.
} \\

\CVItem{2022-2023, \textit{Connecting Semantically Similar Stories using Natural Language Processing}, University of Otago}{
	Ongoing group research project in natural language processing. Goal was to create methods of measuring similarities between documents with respect to different metrics.\\
	Found that similar documents can be clustered together even when presented without that structure.
} \\

\CVItem{2023, \textit{Handwriting Analysis over Dominant vs Non-Dominant Hands}, University of Otago}{
	Ongoing group research project in handwriting analysis. Attempted to classify handwriting quality using a variety of metrics.\\
	Gained experience with data cleaning, signal processing, data visualization, and model comparisons. Currently in the data collection phase.
} \\


\CVItem{2021-2022, \textit{Provenance Tracking }, University of Otago}{
	Summer research project into tracking provenance across different domains. Focus on distributed ledger technologies as a support for event calculus. Found other technologies may be more promising for the role, but current implementation may be sufficient.
} \\

%------------------------------------------------

\clearpage % Start a new page

\userinformation % Print your information in the left column

\framebreak % End of the first column

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\CVSection{Experience}

%------------------------------------------------

\CVItem{2021-2023, \textit{Lab Demonstrating}, University of Otago}{
	Involved presenting computer science topics to students. In later years, also involved creating and refining teaching resources for labs.\\
	Detailed achievements:
	\begin{itemize}
		\item Demonstrated for the papers:
		\begin{itemize}
			\item COSC201: Algorithms and Data Structures
			\item COSC202: Software Development
			\item COSC203: Web, Databases, and Networks
			\item COSC204: Computer Systems and Security
			\item COSC301: Network Management and Security
			\item COSC343: Artificial Intelligence
		\end{itemize}
		\item Gained experience working with a team.
		\item Gained experience communicating difficult concepts to the point of deep understanding.
		\item Gained leadership experience with additional responsibility to creating lab material.
	\end{itemize}
}

\CVItem{2019-2023, \textit{Tutoring}, Freelance} {
	Freelance tutoring for various subjects about the university. Specifically tutored in the fields of Computer Science, Mathematics, and Physics.
}

\Sep % Extra whitespace after the end of a major section


%----------------------------------------------------------------------------------------
%	AWARDS
%----------------------------------------------------------------------------------------

\CVSection{Awards}

%------------------------------------------------

\CVItem{2023, \textit{Master's Research Scholarship}, University of Otago}{Awarded to students with high academic achievement moving into Masters research.}
\\
\CVItem{2021, \textit{Sir George Grey Senior Scholarship}, University of Otago}{Awarded to the top Bachelors student in the Division of Science.}
\\
\CVItem{2021, 2022, \textit{Summer Research Scholarship}, University of Otago}{Awarded to students who undertake a research project over summer.}
\\
\CVItem{2020, \textit{Robert Jack Physics Prize (200 Level)}, University of Otago}{Awarded to the top student in 200-level physics.}
\\
\CVItem{2019, \textit{Academic Excellence Entrance Scholarship}, University of Otago}{Awarded to the students with high academic achievement entering the University of Otago.}
\\
\CVItem{2019, \textit{Gordon Jupp Memorial Prize in Physics}, University of Otago}{Awarded to the top student in 100-level physics.}
\\
\CVItem{2019, \textit{Dux}, Otago Boys High School}{}
%------------------------------------------------

\Sep % Extra whitespace after the end of a major section


%----------------------------------------------------------------------------------------

\end{document}
